Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-29 MS_thesis.tex
Add comment before funding section
Shorten title of appendix B
Make sure microtyping is active throughout
Remove dedication for now
Add dedication page

%Dedication
\dedication{This thesis is dedicated to ?}

@@

\funding{
I am a recipient (Registration no. SX-1711025) of the Kishore Vaigyanik Protsahan Yojana (KVPY) fellowship from the Department of Science and Technology, Government of India, and gratefully acknowledge the same for providing financial support.

@@

\begin{document}
\microtypesetup{disable}
\pagestyle{plain} %Don't make the initial frontmatter fancy

@@

%Enable microtype from here on out
\microtypesetup{enable}

@@

%Import the Appendices
\chapter{From It\^{o} to Fokker-Planck}\label{App_SDE_FPE}
\input{ind_files/99_Appendix_A}
\chapter{Deriving stochastic trait frequency dynamics using It\^{o}'s formula}\label{App_density_to_freq}
\input{ind_files/99_Appendix_B}
\chapter{A Price-like equation for the variance of a type-level quantity}\label{App_stoch_var_eqns}
\input{ind_files/99_Appendix_C}
\chapter{Some Examples}\label{App_examples}
\input{ind_files/99_Appendix_D_examples}

>>>>

%Dedication
\dedication{

	\vspace{-2.5cm}

	\includegraphics[width=\textwidth]{backend/ch_comic_dedication}\\

	\vspace{1.8cm}

	This thesis is dedicated to obeying the inscrutable exhortations of your soul.
	\extrafootertext{\tiny Calvin and Hobbes is the property of Mr. Bill Watterson and Andrews McMeel Syndication. This comic has been reproduced with explicit permission from Andrews McMeel Syndication.}
	}

@@

%Add funding sources here
\funding{
I am a recipient (Registration no. SX-1711025) of the Kishore Vaigyanik Protsahan Yojana (KVPY) fellowship from the Department of Science and Technology, Government of India, and gratefully acknowledge the same for providing financial support.

@@

\begin{document}
%\microtypesetup{disable}
\pagestyle{plain} %Don't make the initial frontmatter fancy

@@

%Enable microtype from here on out
%\microtypesetup{enable}

@@

%Import the Appendices
\chapter{From It\^{o} to Fokker-Planck}\label{App_SDE_FPE}
\input{ind_files/99_Appendix_A}
\chapter{Stochastic trait frequency dynamics using It\^{o}'s formula}\label{App_density_to_freq}
\input{ind_files/99_Appendix_B}
\chapter{A Price-like equation for the variance of a type-level quantity}\label{App_stoch_var_eqns}
\input{ind_files/99_Appendix_C}
\chapter{Some Examples}\label{App_examples}
\input{ind_files/99_Appendix_D_examples}
